Ludwig User Tutorial

### 2022-08-15 docs/tutorial/tutorial.tex

\begin{enumerate}
\item Copy the input file \texttt{input} located in the directory 
\texttt{/docs/tutorial/test2} 
to your working directory. This input file contains the parameters required for this run. 
\item Run the code in your working directory by issuing the command:
\begin{lstlisting}
$ mpirun -np 8 ./Ludwig.exe input
\end{lstlisting}
\item As before, you should now see statistics being reported on your standard output. But 
in this case two sets of output files are being created, one containing the velocity and 
the other compositional order parameter ($\phi$) data at each lattice point in the simulation. 
In this example, these data are in binary format.
\item You are able to use the same exectuable \texttt{extract} from the previous 
example for the  post-processing with different arguments and the \texttt{-k} flag to produce
files in VTK-format:
\begin{lstlisting}
$ ./extract -k vel.001-001.meta vel-00010000.001-001
$ ./extract -k phi.001-001.meta phi-00010000.001-001
\end{lstlisting}
\item A bash script like this one below can be used for convenient post-processing of multiple 
raw data files and time steps (with appropriate start, increment and end in the \texttt{for} loop):
\begin{lstlisting}
#!/bin/bash
for i in `seq 1000 1000 10000`;
do
  tstep=$(printf "%08d" $i)
  ./extract -k vel.001-001.meta vel-${tstep}.001-001  
  ./extract -k phi.001-001.meta phi-${tstep}.001-001
done
\end{lstlisting}
\item You should now see files with the extension \texttt{.vtk} corresponding to the velocity 
and $\phi$ data ready to be visualised using ParaView.
\begin{enumerate}
\item In Paraview open the files containing the $\phi$ data.
\item Click on the group of files in the pipeline browser and apply a contour map using 
Filters/Common/Contour or in the tool bar:

@@

for i in `seq 1000 1000 10000`;

>>>>

\begin{enumerate}
\item Copy the input file \texttt{input} located in the directory 
\texttt{/docs/tutorial/test2} 
to your working directory. This input file contains the parameters required for this run. 
\item Run the code in your working directory by issuing the command:
\begin{lstlisting}
$ mpirun -np 8 ./Ludwig.exe input
\end{lstlisting}
\item As before, you should now see statistics being reported on your standard output. But 
in this case two sets of output files are being created, one containing the velocity and 
the other compositional order parameter ($\phi$) data at each lattice point in the simulation. 
In this example, these data are in binary format.
\item You are able to use the same exectuable \texttt{extract} from the previous 
example for the  post-processing with different arguments and the \texttt{-k} flag to produce
files in VTK-format:
\begin{lstlisting}
$ ./extract -k vel.001-001.meta vel-00010000.001-001
$ ./extract -k phi.001-001.meta phi-00010000.001-001
\end{lstlisting}
\item A bash script like this one below can be used for convenient post-processing of multiple 
raw data files and time steps (with appropriate start, increment and end in the \texttt{for} loop):
\begin{lstlisting}
#!/bin/bash
for i in $(seq 1000 1000 10000);
do
  tstep=$(printf "%08d" $i)
  ./extract -k vel.001-001.meta vel-${tstep}.001-001  
  ./extract -k phi.001-001.meta phi-${tstep}.001-001
done
\end{lstlisting}
\item You should now see files with the extension \texttt{.vtk} corresponding to the velocity 
and $\phi$ data ready to be visualised using ParaView.
\begin{enumerate}
\item In Paraview open the files containing the $\phi$ data.
\item Click on the group of files in the pipeline browser and apply a contour map using 
Filters/Common/Contour or in the tool bar:

@@

for i in $(seq 1000 1000 10000);
